First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-04-23 paper/paper.tex
Some C backend details

\section{C Backend}
\begin{todo}
  Write this section
\end{todo}

@@

>>>>

\section{C Backend}
\begin{todo}
  Expand this section
\end{todo}

@@

This backend is based on a globally unique name generator. Similar to
SSA form, a new C variable is created for each Haskell subexpression.
It differs from SSA, however, in that these variables can be assigned multiple
times. In particular, a variable can be assigned in multiple branches of
an \ttt{if} statement or inside of a \ttt{while} loop. This simplifies
the implementation, as $\phi$ nodes are not needed.

The following \ttt{struct}s provide the C representation for Haskell expressions:

\begin{lstlisting}
typedef enum var_type_tag {
  EXPR_INT
, EXPR_FLOAT
, EXPR_DOUBLE
, EXPR_CHAR
, EXPR_BOOL
, EXPR_CLOSURE
, EXPR_EITHER_LEFT
, EXPR_EITHER_RIGHT
, EXPR_PAIR
, EXPR_UNIT
, EXPR_STEP
, EXPR_DONE
, EXPR_UNBOXED
} var_type_tag;

typedef enum semantic_type_tag {
  NO_SEMANTIC_TAG
, EXPR_COMPLEX     // Complex numbers
} semantic_type_tag;

struct closure_t;

typedef struct var_t {
  var_type_tag tag;
  semantic_type_tag semantic_tag;
  void* value;
} var_t;

typedef struct closure_t {
  var_t* fv_env;
  var_t (*fn)(var_t, struct closure_t*);
} closure_t;
\end{lstlisting}

The \ttt{semantic\_tag} allows type information preserved by the \ttt{Typeable} constraints
in the EDSL to be brought over to the generated C code. In our implementation, this is
used to distinguish between pairs of \ttt{Double}s and \ttt{Complex Double} values. In the
case of a \ttt{Complex Double}, the \ttt{var\_t} would have a \ttt{tag} field with the value
\ttt{EXPR\_PAIR} and a \ttt{semantic\_tag} field with the value \ttt{EXPR\_COMPLEX}.
